\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/parth-srivastava-949742192/}{\Large Parth Srivastava}} & Email : \href{mailto:parth0803@gmail.com}{parth0803@gmail.com}\\
  {\href{https://github.com/savss624}{Github}}, {\href{https://www.linkedin.com/in/parth-srivastava-949742192/}{LinkedIn}}, {\href{https://twitter.com/savss624}{Twitter}} & Mobile : +91 7525044512 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM Institute of Science and Technology}{Chennai, India}
      {Bachelor of Technology in Computer Science;  GPA: 9.72/10.0}{June. 2019 -- May. 2023}
  \resumeSubHeadingListEnd  
  
  
%-----------COURSEWORK-----------------
\section{Coursework}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://ninjasfiles.s3.amazonaws.com/certificate14114222a869819638b05b52e15bd804183246b.pdf}{Data Science and Machine Learning (Coding Ninjas)}}{Delhi, India}
      {Data Cleaning, Data Visualization, Scraping, Statistics, Machine Learning, Deep Learning}{Feb. 2021 -- Aug. 2021}
    \resumeSubheading
   {\href{https://ninjasfiles.s3.amazonaws.com/certificate12026718dde55c9c604fb4e3474a96f40ee9cbd.pdf}{Full Stack Development (Coding Ninjas)}}{Delhi, India}
      {HTML, CSS, JavaScript, Reactjs Nodejs, Expressjs, Mongodb}{July. 2020 -- Dec. 2020}
      
  \resumeSubHeadingListEnd   
  
  
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
   \resumeSubHeadingListStart
    \resumeSubItem{Proficient}
      {Java, Flutter, Python(Numpy, Pandas),  NLP, scikit-learn, Selenium, APIs}
    \resumeSubItem{Familier}
      {HTML, CSS, JavaScript, Reactjs, Nodejs, Expressjs, Tensorflow Keras, Tableau, git}
    \resumeSubItem{Databases}
      {Mongodb, SQL, Firebase}
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Royal Brisbane and Women’s Hospital}{Melbourne, Australia}
      {Software Engineer Intern}{Jul 2021 - Dec 2021}
      \resumeItemListStart
        \resumeItem{\href{https://github.com/Ctrl-Alt-Eliiiteee/POS_nauseum_FrontEnd}{Mobile Application}}
          { I helped making the Mobile Application (both android and IOS) for managing the hospital online.}
        \resumeItem{\href{https://github.com/Ctrl-Alt-Eliiiteee/POS_nauseum_Backend}{Backend APIs}}
          {Worked on APIs for all data retrieving functionalities}
      \resumeItemListEnd
      
      \resumeSubheading
      {HighRadius Corporation}{Remotely, India}
      {Software Engineer Intern}{Jan 2022 - Present}
     \resumeSubHeadingListEnd
  
 
%--------PROJECTS------------
\section{Projects}
   \resumeSubHeadingListStart
   
    \resumeSubheading
     {{\href{https://github.com/savss624/ScholarAid}{ScholarAid}} - {\href{https://drive.google.com/file/d/16FmYzj0ywmVnXxMNeyuHloALYQJkNVQ7/view?usp=sharing}{(SRM Hackathon Project)}}}{Languages: Python, Flutter}
     {Application to make Online Teaching effective and efficient using AI and AR}{}
     \resumeItemListStart
        \resumeItem{My Contributions}
          {I build the question paper generator, question answering model, and paragraph summary generator APIs using famous NLP transformers. Also, build a result data visualizer in the mobile application.}
        \resumeItem{Project Achievement}
          {Awarded with Special Mention Award at SRM Hackathon.}
      \resumeItemListEnd
      
   \resumeSubheading
     {{\href{https://github.com/savss624/ThinkArt}{ThinkArt} }- {\href{https://drive.google.com/file/d/1VC3gtZcvzoB309PDeM0TbuI-0nAfBffA/view?usp=sharing}{(HackTrix Hackathon Project)}}}{Languages: Python, Flutter}
     {Application to support Painting Industry}{}
      \resumeItemListStart
        \resumeItem{My Contributions}
          {I build a mobile application for Painting generation using the DeepDaze algorithm and Painting style conversion tasks like a painting to sketch.}
        \resumeItem{Project Achievement}
          {Awarded with Honourable Mention Award at HackTrix Hackathon.}
        \resumeItem{EchoAR}
          {This project was also mentioned on EchoAR's Inspiration Page.}
      \resumeItemListEnd
    
    \resumeSubheading
     {{\href{https://github.com/savss624/SafeLink}{SafeLink}} - {\href{https://drive.google.com/file/d/1-vXKT2rGWPcYgm0zPiRzo5UukzaXSac-/view?usp=sharing}{(GeeksforGeeks Hackathon Project)}}}{Languages: Python, Flutter}
     {Application for the people who feel unsafe while traveling alone}{}
     \resumeItemListStart
        \resumeItem{My Contributions}
          {I build continuous speech recognizer mobile application through which user can give a specific command for help even if their device is locked.}
       \resumeItem{Project Achievement}
          {Won the GeeksforGeeks Hackathon.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%--------ADDITIONAL INFOMATION------------
\section{Additional Information}
 \resumeSubHeadingListStart
   \resumeSubItem{Other Achievements}
     {Winner of HackYuva Hackathon, SyntHacks, Codestellation.}
   \resumeSubItem{Other Works}
     {{\href{https://github.com/savss624/State-Farm-Distracted-Driver-Detector}{State Farm Distracted Driver Detector}}{\href{https://www.kaggle.com/c/state-farm-distracted-driver-detection/overview}{(Kaggle Competition)}}, {\href{https://github.com/savss624/Gmeet-Automation}{Gmeet Automation}}}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
